An Automatic Verification Framework for Software Configurations

### 2016-05-10 OSDI/intro.tex
ruzica

For practical purposes we use the dataset given at~\cite{configdataset}. Every file in our dataset contains an error, but it is 
always a different error and it only appears in a small percentage of files. Using that insight we were able, with the help of the probabilistic cutoff, to learn an
accurate set of rules. The rules in general specify what properties do variables need to satisfy. One can see this learning process as a
way of deriving  
a specification for configuration files.  Once there is a specification, we can start with formal verification. With these rules we can efficiently check the correctness of the configuration files
of interest and detect potential errors.

The learning process works in two phases. In the first phase, 
\app analyzes the sample dataset and generates a 
well-structured and probabilistically-typed 
intermediate representation. 
In the second phase, \app derives rules and constraints by analyzing
the intermediate representations.  Every learned rule is annotated with a probability depicting in
which percentage of the files the rule was seen as correct. As learned rules we only select those rules whose 
correctness probability is above the set threshold.

Finally, we checks whether a
given variable

>>>>

For practical purposes we use the dataset given at~\cite{configdataset}. Every file in our dataset contains an error, but it is 
always a different error and it only appears in a small percentage of files. Using that insight we were able, with the help of the probabilistic cutoff, to learn an
accurate set of rules. The rules, in general, specify which properties do variables need to satisfy. One can see this learning process as a
way of deriving  
a specification for configuration files.  Once there is a specification, we can do a formal verification. With these 
rules we can efficiently check the correctness of the configuration files
of interest and detect potential errors.

The learning process works in two phases. In the first phase, 
\app analyzes the sample dataset and generates a 
well-structured and probabilistically-typed 
intermediate representation. 
In the second phase, \app derives rules and constraints by analyzing
the intermediate representations.  Every learned rule is annotated with a probability depicting in
which percentage of the files the rule was seen as correct. We only accept those rules whose 
correctness probability is above the given threshold.

Finally, while the learned rules establish correlations between two or more variables, using \app one can also detect whether a
single variable has an appropriate value assigned to it. We do that by measuring the values, that are typically assigned to that variable 
and reporting if the current value deviates too much from the recorded values.
